---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# istacr

<!-- badges: start -->
[![R build status](https://github.com/jlopezper/istacr/workflows/R-CMD-check/badge.svg)](https://github.com/jlopezper/istacr/actions)
[![Codecov test coverage](https://codecov.io/gh/jlopezper/istacr/branch/master/graph/badge.svg)](https://codecov.io/gh/jlopezper/istacr?branch=master)
<!-- badges: end -->

The goal of `istacr` is to provide a wrapper to the [ISTAC api catalog](https://www3.gobiernodecanarias.org/aplicaciones/appsistac/api), allowing the user to obtain the open data from R. 

## Installation

You can install the released version of istacr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("istacr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("eDatos/istacr")
```
## How to use this package

The package offers different functions depending on the resource you want to access. There're three main resources:

- Indicators
- Statistical resources (cubes)
- Structural resources


## Examples

### Indicators

Get a list of all indicators:

```{r example1}
library(istacr)
tst <- get_indicators()
str(tst, max.level = 1)
```

Get information of a specific indicator:

```{r example2}
tst <- get_indicators_code("TURISTAS")
str(tst, max.level = 1)
```

Or about geographical granularities:

```{r example3}
# Get granularities
tst <- get_indicators_geographic_granularities()
tst$items

# Get information about a specific granularity
get_indicators_geographical_values('ISLANDS')
```


### Statistical resources

Get all available cubes:

```{r example4}
tst <- get_datasets()
str(tst, max.level = 1)
```

Only those from a specific maintainer:

```{r example5}
tst <- get_datasets_agency('ISTAC')
str(tst, max.level = 1)
```


### Structural resources

```{r example6}
tst <- istacr::get_structuralresources_codelists()
tst$codelist$id
```


```{r example7}
tst <- get_structuralresources_codelists_agency_resource('ISTAC', 'CL_ABANDONO_CULTIVO')
tst$codelist
```


## Further information

Please find the latest documentation on [CRAN](https://cran.r-project.org/web/packages/istacr/istacr.pdf). In case you want to report a bug, please open an [issue](https://github.com/eDatos/istacr/issues).
